Climate variability indices for ecological and crop models in R: the `climatrends` package

### 2021-03-14 inst/paper/paper.Rmd
update-urls

>Kauê de Sousa^1,2[*]^, Magne Neby^3^, Jacob van Etten^2^, Svein Øivind Solberg^1^  
^1^ Department of Agricultural Sciences, Inland Norway University of Applied Sciences, 2318 Hamar, Norway  
^2^ Bioversity International, 00054 Maccarese, Rome, Italy  
^3^ Department of Forest and Field Sciences, Inland Norway University of Applied Sciences, 2480 Koppang, Norway    
^[*]^ Correspondence should be addressed to: <kaue.desousa@inn.no>

@@

The data used here is available as supplementary material (**zenodo ref**) as `cbean`. This contains a data.frame with a Plackett-Luce grouped rankings, the geographical coordinates of each sampled plot and the planting dates from where each farmer decided to start the experiment. The planting dates differ from each other in the same season. The temperature data used was the land surface temperature MODIS (MYD11A2) [@Wan2015] and is storaged as an array with two layers (1st for the day and 2nd for the night temperatures). Each column corresponds to the dates (from 2015-09-10 to 2017-06-09) and the rows corresponds to the rows in the `cbean` data.frame.

>>>>

\pagenumbering{gobble}

>Kauê de Sousa^1,2[*]^, Jacob van Etten^2^, Svein Øivind Solberg^1^  
^1^ Department of Agricultural Sciences, Inland Norway University of Applied Sciences, 2318 Hamar, Norway  
^2^ Bioversity International, 00054 Maccarese, Rome, Italy    
^[*]^ Correspondence should be addressed to: <kaue.desousa@inn.no>

@@

The data used here is available as supplementary material as `cbean`. This contains a data.frame with a Plackett-Luce grouped rankings, the geographical coordinates of each sampled plot and the planting dates from where each farmer decided to start the experiment. The planting dates differ from each other in the same season. The temperature data used was the land surface temperature MODIS (MYD11A2) [@Wan2015] and is storaged as an array with two layers (1st for the day and 2nd for the night temperatures). Each column corresponds to the dates (from 2015-09-10 to 2017-06-09) and the rows corresponds to the rows in the `cbean` data.frame.
